Threads Considered Harmful

### 2011-07-06 papers/paper1/paper.tex
Temp update.

\begin{itemize}
  \item State
  \item Communication
  \item Asynchrony
  \item Concurrency
\end{itemize}

>>>>

\begin{outline}
\item State
  \begin{outline}
  \item Local state only
  \item Shared state
    \begin{outline}
      \item Impossible in distributed systems
      \item Dangerous in local systems
    \end{outline}
  \end{outline}
\item Communication
  \begin{outline}
  \item Atomic asynchronous message passing
  \item Network sets size of atom (UDP)
  \item Can build reliable streams (TCP)
  \item Local equivalent is passing a value
  \item Model should lend itself to writing protocols
  \end{outline}
\item Asynchrony
  \begin{outline}
    \item Model must have natural support for asynchrony, i.e., event-based
    \item Leads to a more efficient implementation because changed state and enabled actions become obvious
  \end{outine}
\item Concurrency
  \begin{outline}
    \item Reason about systems using non-deterministic interleaving of atomic actions
    \item Model should admit implementations that execute concurrently
  \end{outline}
\item Dynamics
  \begin{outline}
    \item Configuration - Edges in graph of communicating components can change at run-time.
      \begin{outline}
      \item Already required in distributed settings
      \item Not addressed in formal models
      \end{outline}
    \item Extension - Nodes in graph of communicating components can change at run-time.
  \end{outline}
\end{outline}
